\begin{thebibliography}{999}
\addcontentsline{toc}{chapter}{\numberline{}Referências Bibliográficas}
\bibitem{BB:95}
J. W. Barrett and J. F. Blowey~(1995),  
{\it An error bound for the finite element approximation of the Cahn-Hilliard equation with logarithmic free energy}, 
Numerische Mathematics, 
{\bf 72}, pp~1--20.

\bibitem{BB:97}
J. W. Barrett and J. F. Blowey~(1997),  
{\it Finite element approximation of a model for phase separation of a multi-component alloy with non-smooth free energy}, 
Numerische Mathematics, 
{\bf 77}, pp~1--34.

\bibitem{BB:99a}
J. W. Barrett and J. F. Blowey~(1999a),  
{\it An improve error bound for finite element approximation of a
model for phase separation of a multi-component alloy}, 
IMA J. Numer. Anal.  
{\bf 19}, pp~147-168.

\bibitem{Cia:78}
P. G. Ciarlet~(1978),
{\bf The Finite Element Method for Elliptic Problems}, 
North-Holland. 

\bibitem{Li:69}
J. L. Lions~(1969),
{\bf Quelques M\'othodes de R\'esolution
des Probl\'emes aux Limites}, 
Dunod.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{pag:13}
Pagnano, A.; Höpf, M.; Teti, R. {\bf A roadmap for automated power line inspection. Maintenance and repair.} 8^th Conference on Intelligent Computation in Manufacturing Engineeering, p.234-239, 2013.

\bibitem{bro:10}
Brochu, E.; Cora, V. M.; De Freitas, N. {\bf A tutorial on bayesian optimization of expensive cost function, with application to active user modeling and hierarchical reinforcement learning.} University British Columbia, Tech. Rep., 2010.

\bibitem{sou:14}
Souza, Jefferson R. {\bf Navegação autônoma para robôs móveis usando aprendizado supervisionado.} Tese de doutorado. Instituto de Ciências Matemáticas e de Computação - ICMC-USP, 2014.

\bibitem{mar:09}
Marsland, S. {\bf Machine Learning: An algorithm perspective.} Chapman \& Hall/CRC, 2009.

\bibitem{asm:13}
Asmuth, John T. {\bf Model-based Bayesian Reinforcement Learning with Generalized Priors.} Tese de doutorado. State University of New Jersey, 2013.

\bibitem{ben:12}
Benicasa, Alcides X. {\bf Navegação autônoma de robôs baseada em técnicas de mapeamento e aprendizagem de máquina.} Revista Brasileira de Computação Aplicada (ISSN 2176-6649), v.4, n.1, p.102-111, março, 2012.

\bibitem{bra:09}
Brandão, M. P., Kienitz, K. H. K., Rangel B. K. {\bf Sistema de Inspeção de Linhas de Transmissão de Energia Elétrica Utilizando Veículos Aéreos Não-Tripulados.} 3rd CTA-DRL Workshop on Data Analysis & Flight Control, September 14 - 15, 2009.

\bibitem{ons:06}
ONS (2006), {\bf “Dados Relevantes 2006: Operação do Sistema Interligado Nacional”}, ONS - Operador Nacional do Sistema Elétrico.

\bibitem{mou:15}
Mourão, Miguel A. M., Lima II, Eduardo J., Bracarense, Alexandre Q., Gontijo, Roberto A., Bomfim, Marcelo H. S., Reis, Marco A., Nascimento, Samy M., Almeida, Cleber V. R., Alcantara, Pedro X., Lepikson, Herman A. 
{\bf Robô de Inspeção de Linha - D311.}
 VII Congresso de Inovação Tecnológica em Energia Elétrica, August 17 - 19, 2015.
 
\end{thebibliography}




